\appendix

\section{Notation index}
\label{sec:appendix-notation}

\begin{longtable}{p{0.20\textwidth}p{0.74\textwidth}}
\toprule
Symbol & Meaning \\
\midrule
\endfirsthead
\toprule
Symbol & Meaning \\
\midrule
\endhead
\bottomrule
\endfoot
$[n]$, $U$ & finite ground set, $|U|=n$ \\
$\powset$, $\cube$ & power set / Boolean cube on $[n]$ \\
$\F$ & a family; union-closed (Sec.~\ref{sec:combinatorial}) or intersection-closed (Sec.~\ref{sec:cohomology}ff.) \\
$\F_x$, $\F_{\bar x}$ & members containing / not containing $x$ \\
$\bias_x$ & bias $|\F_x|-|\F_{\bar x}|$; Frankl: some $\bias_x\ge0$ (union form) / $\le0$ (intersection form) \\
$a(x)$, $c(\F)$ & abundance $|\F_x|/|\F|$; centroid, $c(\F)_x=a(x)$ \\
$\sigma_x$ & coordinate toggle $A\mapsto A\bigtriangleup\{x\}$ \\
$G(\F)$ & transport graph: subgraph of $\cube$ induced on $\F$ \\
$M_x$ & $x$-transport matching (direction-$x$ edges of $G(\F)$) \\
$\F^{\stuck}_x$, $\F^{\stuck}_{\bar x}$ & members needing / rejecting $x$ \\
$\tau$, $\F^c$ & flip $\tau(A)=[n]\setminus A$; flipped family \\
$\walsh S$ & Walsh character $\walsh S(A)=(-1)^{|S\cap A|}$; level $|S|$ \\
$\widehat{\mathbf1_\F}$ & Walsh--Fourier transform of the family indicator \\
$W$, $k$ & minimal generator; $k=|W|=m(\F)$, the open regime is $k\ge3$ \\
$\F^S$ & trace-class $\{A\in\F:A\cap W=S\}$ \\
$\phi(S)$, $\Phi(\G)$ & potential $2|S|-k$; $\Phi(\G)=\sum_{S\in\G}\phi(S)$ \\
$\sigma(W)$ & per-generator target $\sum_{x\in W}\bias_x$ \\
$\mathcal R_S$, $\mathcal S(R)$ & $S$-fibre; co-fibre \\
$\mathcal R_W^{\mathrm{lg}}$ & large fibres $\{R:|R|>\lfloor k/2\rfloor\}$ \\
$\widetilde{\mathcal R}_S$, $q_S$, $d_S$ & cumulative fibre; its size; trace-defect $q_S-|\F^S|$ \\
$Q(W)$, $D(W)$ & monotone part $\langle q,\phi\rangle\ge0$; trace-defect $\langle d,\phi\rangle$; $\sigma(W)=Q(W)-D(W)$ \\
$\bar\jmath_R$, $\delta_R(S)$ & defect retraction; deficiency $S\setminus\bar\jmath_R(S)$ \\
$\mathcal D(R)$, $B(R)$ & co-fibre defect; boundary-edge count \\
$\mathcal W$, $N$, $\Gamma$ & set of minimal generators; $N=|\mathcal W|$; far-pair graph \\
$\Cn$ & category of pointed intersection-closed families, trace morphisms \\
$X(\F)$, $\Xn$ & cubical Walsh-defect complex; $\hocolim_{(\Cn)^{\mathrm{op}}}X(\F)$ \\
$\Gamma_n$ & hyperoctahedral group $(\Z/2)^n\rtimes\Sym_n$ \\
$\isotype Sk$ & $\walsh S$-isotype multiplicity complex in degree $k$ \\
$\BK^{p,q}$, $\Tot$ & Bousfield--Kan double complex; total complex \\
$\mathrm{db}$, $\rho_n$ & doubling functor; trace projection \\
$\Dx$ & matched-in-$x$ subcategory; $X(\Dx)\cong\Xnm\times I$ \\
$\iota^{\cap}_n$, $\delta^{\cap}_n$ & canonical inclusion $\Xn\hookrightarrow X^{\cap}_{n+1}$; cofiber connecting map \\
$h$, $h_x^{\mathrm{tw}}$ & cubical-bridge null-homotopy; twisted bridge \\
$\Fstar$ & minimal counterexample (all $\bias_x>0$) \\
$U_x$, $\fobs$, $m_{xy}$ & rare-coordinate stratum; \v{C}ech sheaf; mismatch cochain \\
$\ob(\Fstar)$ & obstruction class in $\widetilde H^{n-1}(\Xn;\Q)$ \\
$\sgn_{\Sym_n}$ & sign representation of $\Sym_n$ \\
$\cofib\iota_x$ & homotopy cofiber $\Xn/\Xnm$ \\
$Y_1$, $Y_2$ & lower-Walsh vanishing (open); obstruction-class landing (mechanism-sound) \\
\end{longtable}

\section{Component status ledger}
\label{sec:appendix-status}

The table records the verified standing of each load-bearing component
and its source note in the UC1--UC14 ledger. ``Proved'' means a
referee-grade or machine-checked proof exists; ``mechanism-sound''
means the argument's mechanism is verified but a faithfulness input
remains; ``reduced'' means correctly reduced to a named open object;
``open'' means no valid proof exists; ``false'' means provably
refuted.

\begin{longtable}{p{0.27\textwidth}p{0.13\textwidth}p{0.52\textwidth}}
\toprule
Component & Status & Note \\
\midrule
\endfirsthead
\toprule
Component & Status & Note \\
\midrule
\endhead
\bottomrule
\endfoot
Transport identity (Prop.~\ref{prop:transport-identity}) & Proved & UC1; elementary. \\
Globalisation defect orthogonal (Prop.~\ref{prop:globalisation-orthogonal}) & Proved & UC2; disciplines the arc. \\
Trace-partition theorem (Thm.~\ref{thm:trace-partition}) & Proved & UC2; settles $m(\F)\le2$ natively. \\
Large-fibre localisation (Thm.~\ref{thm:uc3-localisation}) & Proved & UC3. \\
Up-closure decomposition / interlock (Thm.~\ref{thm:uc4-interlock}) & Proved & UC4; isolates $D(W)$. \\
Boundary conservation law (Thm.~\ref{thm:boundary-conservation}) & Proved & UC6. \\
No per-fibre sign theorem (Prop.~\ref{prop:no-per-fibre}) & Proved & UC6; genuine impossibility result. \\
Lever-signing on structured classes & Proved & UC7--UC8; settles a hierarchy, not all families. \\
Combinatorial residual (boundary inequality) & Open & terminal residual of the combinatorial arc. \\
U1 wall / direct functorial proof & False route & UC9; pullback is family-independent. \\
Walsh decomposition (Thm.~\ref{thm:walsh-decomposition}) & Proved & UC10; Maschke, not in dispute. \\
Sphere-concentration target UC10.1 (Conj.~\ref{conj:uc10-1}) & Open & UC10; depends on $Y_1$ + $R3$. \\
Trace-injectivity (Thm.~\ref{thm:trace-injectivity}) & Proved & UC12; unconditional; machine-checked clean. \\
Non-vanishing / Fact One (Thm.~\ref{thm:fact-one}) & Proved$^\ast$ & UC11; $\ast$ modulo UC11 Lemma 6.1 faithfulness (Rem.~\ref{rem:wrapper-risk}). \\
$Y_2$ obstruction-class landing & Mechanism-sound & UC13 \S2.4.1; machine-checked (Thm.~\ref{thm:y2-mechanism}); no-cup-product input remains. \\
$Y_1$ lower-Walsh vanishing & Open / reduced & UC10 \S5.3 / UC13 \S4.5; proof invalid (Corr.~\ref{corr:trace-exact}); reduced (Thm.~\ref{thm:y1-reduction}, Res.~\ref{res:y1}). \\
UC14 $R2$ chain-isomorphism & False & Corr.~\ref{corr:r2}; transports the sphere class into a zero group. \\
UC14 $R1$ abutment identification & Provisional & not re-audited. \\
UC14 $R3$ top-Walsh concentration & Method-sound & cofiber-LES + induction; soft spots noted. \\
Closing contradiction (UC13 \S7) & Conditional & valid modulo $Y_1$; internal ``green'' banner withdrawn. \\
Lean \texttt{Frankl\_Holds} (general) & Axiom-dependent & rests on \texttt{case3\_ss\_obstruction\_paper\_axiom} = Frankl (Prop.~\ref{prop:axiom-is-frankl}). \\
Lean concrete $n=3,4$ (full powerset) & Proved & unconditional, axiom-free, machine-checked. \\
Lean isotype encodings & Answer-steered & not citable as evidence (Sec.~\ref{ssec:answer-steered}). \\
\end{longtable}

\section*{Acknowledgement of provenance}
\addcontentsline{toc}{section}{Acknowledgement of provenance}

The mathematical content consolidated here was developed in the
internal notes UC1--UC14 and audited in four further notes
(the $Y_2$ determination, the $Y_1$ audit, the $Y_1$ re-derivation, and
the axiom-restructure investigation). This paper is a consolidation and
correction of that ledger, not new research. The two structural inputs
imported from the sibling $1/3$--$2/3$ program
(Remark~\ref{rem:external-input}, Section~\ref{ssec:u1-wall}) are used
as black boxes and flagged at the point of use. The internal
verdict banners attached to UC13 (``Frankl closes unconditionally'')
and UC14 (``$R1+R2+R3$ all closed'') are \textbf{withdrawn} by this
consolidation; the corrected status is the ledger of
Appendix~\ref{sec:appendix-status}.
